\chapter{Overview}
\label{chapter:overview}
  This chapter outlines the motivation behind this project and the resulting high level goals, as well as roughly what tasks the project was split into.

  \section{Motivation}
    In secondary school, I remember taking drama and dance lessons for three years. This was not my choice. I had no interest, nor any aptitude for dance. To this day I have not benefitted from those lessons, and at this point I can't even recall any information I may have picked up during them. For me, those lessons were a waste. Not only were they a waste, they were highly unpleasant for me.

    This negative experience is just one example of the many problems I've encountered during my education. The longer I've been in education the more this has been on my mind. During a holiday to the countryside of Wales in 2013, instead of relaxing, I started thinking about how courses and their underlying concepts were structured. I drew some diagrams which later formed the basis for the beginning of this project.

    In 2014, I had to interrupt my degree. I consider the various problems in education that I've encountered partially responsible for that, as it left me very disillusioned with my education. In the time I spent off university I reflected further on my experiences and decided that I should do something to try and improve things.

    I have seen far too many people experience great stress from their education, as well as being completely put of continuing to study anything. I've also experienced this, and as my opening paragraph shows, I've had large portions of my time wasted. I would like this to change.

  \section{Goals}
    Based on my motivations, I identified three high level goals to guide the content of my project:

    \begin{enumerate}
      \item To explore the structure of human knowledge: I'm interested in how different subjects are linked, how much knowledge different people have and exactly what I would have to study in order to learn a given subject.

      \item To improve the quality of education: I'd like others to have an easier time than I have. I'm concerned that some people are so disillusioned by their experiences that they give up on education as soon as they are able to.

      \item To improve the accessibility of education: I'd like to make it easier for me to continue studying things independently. It would also be nice to make it easier for people who cannot commit to full time study able to continue learning on their own terms.
    \end{enumerate}

  \section{Project Structure}
    The project is split into three distinct parts:
    \begin{enumerate}
      \item A review of current educational practices, in order to identify some of the main problems that need tackling.
      \item Development of a model of the learning process which can be applied to help solve the issues identified in the review.
      \item The design and implementation of a prototype web application, meant to help test the effectiveness of the model.
    \end{enumerate}
