\chapter{Software Evaluation}
\label{chapter:software_evaluation}
  This chapter details the testing done on the final system, as well as some proposals for the underlying model could be tested in the long term.

  \section{Unit Testing}
    \todo{
      \item Tests cover the views and controllers
      \item Didn't get around to writing basic ops, so no tests for that
      \item Didn't test the db connection: No experience setting up tests when services need to be running in the background
      \item Didn't test that the ogm worked for the smae reasons as above
    }

  \section{Usability Testing}
    \todo{
      \item I tested in myself, but since the minimum features weren't implemented there was little point in doing usability testing
      \item Graph viewer has some problems: The force based layout doesn't always result in a very readable graph and needs some serious tweaking: Graph display is a whole problem of its own: Extension, grouping nodes together to simplify the display
    }

  \section{Results}
    \todo{
      \item Created a way to view a graph
      \item Graph can be edited only through external tools
      \item Didn't implement the basic operations (I managed to for the old model, but that became obsolete so it was dropped)
      \item Overall I feel the software implementation was functionally a failure, though personally, I gained a lot of experience from it: It wasn't a waste, but if I went back I'd have focussed heavily on the model and spent my time on constructing tests of that.
    }

  \section{Lessons Learned}
    \todo{
      \item Should have had a learning period dedicated to learning tools and techniques for web dev: Should have expected not to produce anything for a while, just run through tutorials making test sites. Would have been less stressed and unhappy about progress: Would probably have had more energy to work: Stress made me sour to the work
      \item Should have focussed more heavily on the model and testing that. Late but necessary changes to the model made some work invalid. The software I produced should only have become the focus once I had a solid model to test.
      \item Perhaps a graph viewing tool would have been more useful as implementations already exist, just not a recorded structure. I was too focussed on producing a useful tool when I should have realised the model itself was useful and a prerequisite or the tools
      \item I felt as though I had to produce a peice of software: Clearly this was a mistake on my part.
    }
